\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-08 poster/main.tex
update poster

\begin{block}{Objectives}
\begin{columns} % Subdivide the first main column
\begin{column}{.6\textwidth}
\noindent Design a mechanism that achieve differential privacy by scaling to a metric between distribution.
\begin{enumerate}
\item A differentially private bayesian mechanism,
\item Calibrating mechanism noise by the same probabilistic distance we want to measure accuracy with.
\item Applying smooth sensitivity in mechanism to achieve better accuracy.
\end{enumerate}
\end{column}
\begin{column}{.4\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{poster_0.eps}
\caption{Hellinger Sensitivity}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Bayesian Inference Background}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
Conjugate prior distribution, $\betad(\alpha, \beta)$, with hyper parameters $\alpha,\beta\in\mathbb{R}^{+}$;

Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$;

Bernoulli likelihood function: $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;

Posterior distribution derived: 
$\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.

\end{block}
% and with p.d.f:

@@

In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,

@@

Producing an element $r$ in $\betaset$ with:
$
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
\frac 
{exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
$,
(given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$).

\begin{itemize}
  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.

  \item[-] $-\hellinger(\bysinfer(\dataobs),r)$, the scoring function instantiated by Hellinegr distance.

  \item[-] $S(\dataobs)$, the smooth sensitivity:
  $
  S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\}
  $,
  where
  \begin{itemize}
   \item $d$: Hamming distance between two datasets,

>>>>

\begin{block}{Objectives}
\begin{columns} % Subdivide the first main column
\begin{column}{.65\textwidth}
\noindent Design a differentially private Bayesian inference mechanism by scaling to a metric between distribution.
\begin{enumerate}
\item A differentially private Bayesian mechanism,
\item Calibrating mechanism noise by the same probabilistic metric we want to measure accuracy with.
\item Applying smooth sensitivity in mechanism to achieve better accuracy. This is motivated by the Fig. \ref{fig_sensitivity} that local sensitivity is very steep in edge but very smooth in center part.
\end{enumerate}
\end{column}
\begin{column}{.3\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{poster_0.eps}
\caption{Hellinger Sensitivity}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Bayesian Inference Background}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
Conjugate prior distribution, $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$;
\begin{itemize}
  \item[-] Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$;

  \item[-] Bernoulli likelihood function: $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;

  \item[-] Posterior distribution derived: $\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
\end{itemize}
\end{block}
% and with p.d.f:

@@

In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.

@@

Producing an element $r$ in $\betaset$ with:
$
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
\frac 
{exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
$,
given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$.

\begin{itemize}
  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$;

  \item[-] $-\hellinger(\bysinfer(\dataobs),r)$, the scoring function instantiated by Hellinegr distance;

  \item[-] $S(\dataobs)$, the smooth sensitivity:
  $
  S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\}
  $,
  where:
  \begin{itemize}
   \item $d$: Hamming distance between two datasets,
